---
output:
  github_document:
    html_preview: false
---

# mcreplicate: Multi-Core Replications

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/christophergandrud/mcreplicate/workflows/R-CMD-check/badge.svg)](https://github.com/christophergandrud/mcreplicate/actions)
<!-- badges: end -->

**mcreplicate** adds multi-core functionality to R's `replicate` function. It allows easy parallelization on all platforms, including on Windows.


## Installation

Install the package from GitHub:

```r
if (!require(remotes)) install.packages("remotes")
remotes::install_github("christophergandrud/mcreplicate")
```

## Use

`mc_replicate()` works just like `replicate()`, but distributes the replications on multiple cores

```{r}
library(mcreplicate)

# Function to replicate
one_sim <- function(n, control_prob, rel_effect) {
  treat_prob <- control_prob + (control_prob * rel_effect)
    
  cy <- rbinom(n = n, size = 1, prob = control_prob)
  ty <- rbinom(n = n, size = 1, prob = treat_prob)
  
  mean(ty) - mean(cy)
}

diff_means <- mc_replicate(10, one_sim(n = 100, control_prob = 0.1, 
                                      rel_effect = 0.01))

diff_means
```

### Windows users

On Windows, **mcreplicate** relies on a parallel socket cluster backend. This requires the user to explicitely specify which packages and variables should be used to populate the workers' environments. By default, **mcreplicate** attaches all currently loaded packages and all variables from the current environment which do not start with a ".". This can be changed using the `packages`, `varlist` and `envir` optional arguments. You can learn more on the function's help file.

#### Example

```{r, eval=FALSE}
k = 2

# The following works as intended, since the variable "k" is exported by 
# default to each worker.
mc_replicate(10, rnorm(k))

# For a reduced overhead, you can specify to *only* export the variable "k" 
# from the current environment and to not load any particular package.
mc_replicate(10, rnorm(k), packages=NULL, varlist=c("k"), envir=environment())
```

## References

This is inspired by the `mcreplicate` function from the [rethinking](https://github.com/rmcelreath/rethinking) package.

